Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
remove section
comment that section back in
add in countries again

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Mild censorship} 
%(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Reaching these 
domains requires any use of a censorship circumvention 
tool. The default option to ``connect'' to the Tor network 
directly will circumvent this censor. Additional correct
bridge or proxy configuration are optional. 
\item {\bfseries Intermediate censorship} 
%(Reflective of countries such as {\color{red}?? and ??}.)
Certain domain names are blocked. Censorship circumvention
tools are blocked. Since Tor is blocked by blocking all public Tor
relay nodes, the default option to ``connect'' to the Tor network
directly will fail. A choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
or a valid non-public bridge is required to circumvent this censor.  
Additional correct proxy configuration is optional.
\item {\bfseries Comprehensive censorship} 
%(Reflective of countries such as China and Syria.)
Certain domain names are blocked. Censorship circumvention tools
are thoroughly blocked. Tor is blocked by blocking all public
Tor relay nodes, and the censor has examined source code to block
all hard-coded bridge relays in the configuration interface. The default option
to ``connect'' to the Tor network directly will fail. Choosing any bridges other than
``meek-amazon,'' ``meek-azure,'' and ``meek-google,'' will fail. This is because 
domain-fronting requires censors to block entire CDNs to also block this
transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments.
(See ~\cite{fifield2015blocking} for additional details.)\\
\end{itemize}

@@

\noindent {\bfseries Improved and Alternative Interfaces} {\color {red} blah blah}

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Mild censorship} 
(Reflective of countries such as France and Australia.)
Certain domains are blocked. Reaching these 
domains requires a censorship circumvention 
tool. The default option to ``connect'' to the Tor network 
directly will circumvent this censor. Additional correct
bridge or proxy configurations are optional. 
\item {\bfseries Intermediate censorship} 
(Reflective of countries such as Tunsia.)
Certain domains are blocked. Censorship circumvention
tools are blocked. Since Tor is blocked by blocking all public Tor
relay nodes, the default option to ``connect'' to the Tor network
directly will fail. Any choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
or a valid non-public bridge will circumvent this censor.  
Additional correct proxy configuration is optional.
\item {\bfseries Comprehensive censorship} 
(Reflective of countries such as China and Syria.)
Certain domains are blocked. Censorship circumvention tools
are thoroughly blocked. Tor is blocked by blocking all public
Tor relay nodes, and the censor has examined source code to block
all hard-coded bridge relays in the configuration interface. The default option
to ``connect'' to the Tor network directly will fail. Choosing any bridges other than
``meek-amazon,'' ``meek-azure,'' and ``meek-google,'' will fail. This is because 
domain-fronting requires censors to block entire CDNs to also block this
transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments.
(See ~\cite{fifield2015blocking} for additional details.)\\
\end{itemize}

@@

%\noindent {\bfseries Improved and Alternative Interfaces} {\color {red} optional section here.}
